---
title: "Report: a glimpse into genetics of height using openSNP data"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(drake)
library(tidyverse)
```

Running `make(plan)` will generate a hidden folder called `.drake/`. 

There are two main drake functions that allow us to retrieve the drake objects created in the `plan` object in `make.R`: 

- `readd(plan)`: 
- `loadd(fit)`:

## Data

We can access the plot with `readd()`.

```{r plot, fig.width = 6, fig.height = 10}
readd(plot)
```

## Results

First we load the two linear regression models using `loadd()`:

```{r load-fits}
loadd(fit.multiple)
loadd(fit.simple)

```

### Simple linear regression

`lm(height ~ genotype_i)`, for the genotypes `r paste(unique(fit.simple$genotype), collapse = ", ")`.

The lm coefficients are in table \@ref(tab:results-simple).

```{r results-simple}
fit.simple %>% 
  knitr::kable(format = "latex", 
               caption = "Simple linear regression results.")
```

### Multiple linear regression

`lm(height ~ genotype1 + genotype2 + ...) %>% step()`, for the genotypes `r paste(unique(fit.simple$genotype), collapse = ", ")`.

The lm coefficients are in \@ref(tab:multiple).

```{r results-multiple}
fit.multiple %>% 
  knitr::kable(format = "latex", 
               caption = "Multiple linear regression results after AIC.")
```
